LHC abort gap monitor electronics upgrade

### 2024-03-13 bibliography.tex
added new literature

>>>>

        \bibitem{bsra_calib} A. Boccardi et a1., \emph{Calibration procedures and
            automated actions for the Abort Gap Monitors of LHC}, (2015, 3), LHC-B SRA-
            ES-OOOl, \url{https:edms.cern.ch/document/1337184/1}

        \bibitem{Fisher_bsra}Fisher, A. \emph{Expected Performance of the LHC
            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).}
            (CERN,2010), \url{https://cds.cern.ch/record/1261191}

        \bibitem{particles_in_ag}Meddahi, M., Bart Pedersen, S., Boccardi, A.,
            Butterworth, A., Fisher, A., Gianfelice-Wendt, E., Goddard, B., Hemelsoet,
            G., Höfle, W., Jacquet, D., Jaussi, M., Kain, V., Lefevre, T., Shaposhnikova,
            E., Uythoven, J. \& Valuch, D. LHC Abort Gap Monitoring and Cleaning.
            (2010,6), \url{https://cds.cern.ch/record/1277630}

        % https://cds.cern.ch/record/2295107/files/1638883_171-176.pdf
        \bibitem{machine_protect}Bravin, E., Belohrad, D., Calvo, E. \& Mazzoni, S. Beam
            instrumentation for machine protection.  (2014), \url{https://cds.cern.ch/record/2295107}

        % https://cds.cern.ch/record/1261191/files/performance-note-014.pdf
        \bibitem{expected_performance_bsrt}Fisher, A. Expected Performance of the LHC
            Synchrotron-Light Telescope (BSRT) and Abort-Gap Monitor (BSRA).
            (CERN, 2010, 3), \url{https://cds.cern.ch/record/1261191}

% other sources
% https://indico.cern.ch/event/359810/contributions/853246/attachments/716754/983942/BSRA_BI_TB_Feb2015.pdf
